Capstone Movielens Report

### 2025-05-16 reports/capstone-movielens.site/02.5.UME-model.Rmd
RMD report: minor refactoring (troubleshooting cross-references)

::: {.noteblock data-latex=""}
The function described above accepts the `lambda` parameter, which we will need later for the _Regularization_ method. We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need later for the *Regularization* techniques (for details, see the [mean_reg](#func.mean_reg) function description in the [Appendix](#appendix.a) of this report).
We will explain that later in the [Regularization Method] section. 
For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. In this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
:::

@@

::: {.noteblock data-latex=""}
Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the
[Appendix](#appendix.a) of this report).
:::

@@

### Regularizing User+Movie Effect Model
\

@@

We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Appendix](#appendix.a) of this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter:

@@

::: {.noteblock data-latex=""}
We use the custom data visualization function [data.plot](#func.data.plot) described in the [Appendix](#appendix.a.data_helper.functions) of this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script.
:::

>>>>

::: {.noteblock data-latex=""}
The function described above accepts the `lambda` parameter, which we will need later for the _Regularization_ method. We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] section).
We will explain that later in the [Regularization Method] section. 
For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. In this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
:::

@@

::: {.noteblock data-latex=""}
Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the
[Appendix](#appndx_a) of this report).
:::

@@

### User+Movie Effect Model Regularization
\

@@

We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Appendix](#appndx_a) of this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter:

@@

::: {.noteblock data-latex=""}
We use the custom data visualization function [data.plot](#func.data.plot) described in the [Appendix](#appndx_a.data_helper.functions) of this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script.
:::

### 2025-05-16 reports/capstone-movielens.site/04.appendix.Rmd
RMD report: minor refactoring (troubleshooting cross-references)

# Appendix {#appendix.a}
## Data Helper Functions {#appendix.a.data_helper.functions}
\

@@

::: { #func.data.plot.params .sidebar }
#### Parameters
\
::: { #func.mean_reg.params.param1s .sidebar }
  - **param1:** description;

@@

## Regularization: Common Helper Functions
\

@@

::: { #func.fname00.params .sidebar }
#### Parameters
\
::: { #func.mean_reg.params.param1s .sidebar }
  - **param1:** description;

>>>>

# Appendix {#appndx_a}
## Data Helper Functions {#appndx_a.data_helper.functions}
\

@@

::: { #func.data.plot.params .sidebar }
#### Parameters
\
::: { #func.mean_reg.params.param1 .sidebar }
  - **param1:** description;

@@

## Regularization: Common Helper Functions {#appndx_a.rglr.common_helper.functions}
\

@@

::: { #func.fname00.params .sidebar }
#### Parameters
\
::: { #func.fname00.params.param1 .sidebar }
  - **param1:** description;

:::
::: { #func.fname00.params.param2 .sidebar }
  - **param2:** description.
